### 2013-11-20 regressionModelling.Rmd
Just another test commit whether rawgithub can handle with .css ver2

% Regression modellining

@@

htmlreg(list(unbisoc.1,unbisoc.2,
             unbisoc.3,unbisoc.4,
             unbisoc.5,unbisoc.6),
        custom.model.names = model.names,
        custom.coef.names = coef.names,
        inline.css = FALSE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
       caption="Simple logistic regression on social blame", caption.above=TRUE)

@@

```{rUnilevelBivarIndOutput, results='asis'}
library(texreg)
htmlreg(list(unbiind.1,unbiind.2,
             unbiind.3,unbiind.4,
             unbiind.5,unbiind.6),
        custom.model.names = model.names,
        custom.coef.names = coef.names,
        inline.css = FALSE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
       caption="Simple logistic regression on individual blame", caption.above=TRUE)
```

@@

```{rUnilevelMulvarSocOutput, results='asis'}
library(texreg)
htmlreg(list(mulbisoc.1,mulbisoc.2,
             mulbisoc.3,mulbisoc.4,
             mulbisoc.5,mulbisoc.6),
        custom.coef.names = coef.names,
        inline.css = FALSE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
       caption="Multiple logistic regression on social blame", caption.above=TRUE)

@@

```{rUnilevelMulvarIndOutput, results='asis'}
library(texreg)
htmlreg(list(mulbiind.1,mulbiind.2,
             mulbiind.3,mulbiind.4,
             mulbiind.5,mulbiind.6),
        custom.coef.names = coef.names,
        inline.css = FALSE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
       caption="Multiple logistic regression on individual blame", caption.above=TRUE)
```

@@

library(texreg)
htmlreg(list(bisoc.1,bisoc.2,
          bisoc.3,bisoc.4,
          bisoc.5,bisoc.6,
          bisoc.8,
          bisoc.9,bisoc.10,
             bisoc.11,bisoc.12,
             bisoc.13),
        custom.coef.names = coef.names.multi,
        naive = TRUE,
        inline.css = FALSE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        include.pvalues=TRUE,
        caption="Bivariate social blame", caption.above=TRUE)

@@

library(texreg)
htmlreg(list(biind.1,biind.2,
          biind.3,biind.4,
          biind.5,biind.6,
          biind.8,
          biind.9,biind.10,
          biind.11,biind.12,
             biind.13),
        custom.coef.names = coef.names.multi,
        naive = TRUE,
        inline.css = FALSE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        use.packages=FALSE,
        include.pvalues=TRUE,
        caption="Bivariate individual blame", 
        caption.above=TRUE)

@@

htmlreg(list(soc.0,
        soc.1,
        soc.2,
        soc.3,
        soc.4),
        custom.model.names = model.names.multi,
        custom.coef.names = coef.names.multi,
        naive = TRUE,
        inline.css = FALSE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        include.pvalues=TRUE,
        caption="Logistic multilevel random intercept model for social blame type of explanation", 
        caption.above=TRUE)

@@

```{rmultilevelMultiIndOutputNOCI, results='asis'}
htmlreg(list(ind.0,
       ind.1,
       ind.2,
       ind.3,
       ind.4),
        custom.model.names = model.names.multi,
        custom.coef.names = coef.names.multi,
        naive = TRUE,
        ci.test = NULL,
        inline.css = FALSE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        include.pvalues=TRUE,
        caption="Logistic multilevel random intercept model for individual blame type of explanation", 
        caption.above=TRUE)

@@

library(texreg)
htmlreg(list(soc.4,ind.4,socVsInc),
        naive = TRUE,
        custom.model.names = model.names.multi.2,
        custom.coef.names = coef.names.multi,
        inline.css = FALSE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        include.pvalues=TRUE,
        caption="Logistic multilevel random intercept model for social and individual blame type of explanation", 
        caption.above=TRUE)
```

>>>>

# Regression modellining

@@

htmlreg(list(unbisoc.1,unbisoc.2,
             unbisoc.3,unbisoc.4,
             unbisoc.5,unbisoc.6),
        custom.model.names = model.names,
        custom.coef.names = coef.names,
        inline.css = TRUE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
       caption="Simple logistic regression on social blame", caption.above=TRUE)

@@

```{rUnilevelBivarIndOutput, results='asis'}
library(texreg)
htmlreg(list(unbiind.1,unbiind.2,
             unbiind.3,unbiind.4,
             unbiind.5,unbiind.6),
        custom.model.names = model.names,
        custom.coef.names = coef.names,
        inline.css = TRUE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
       caption="Simple logistic regression on individual blame", caption.above=TRUE)
```

@@

```{rUnilevelMulvarSocOutput, results='asis'}
library(texreg)
htmlreg(list(mulbisoc.1,mulbisoc.2,
             mulbisoc.3,mulbisoc.4,
             mulbisoc.5,mulbisoc.6),
        custom.coef.names = coef.names,
        inline.css = TRUE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
       caption="Multiple logistic regression on social blame", caption.above=TRUE)

@@

```{rUnilevelMulvarIndOutput, results='asis'}
library(texreg)
htmlreg(list(mulbiind.1,mulbiind.2,
             mulbiind.3,mulbiind.4,
             mulbiind.5,mulbiind.6),
        custom.coef.names = coef.names,
        inline.css = TRUE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
       caption="Multiple logistic regression on individual blame", caption.above=TRUE)
```

@@

library(texreg)
htmlreg(list(bisoc.1,bisoc.2,
          bisoc.3,bisoc.4,
          bisoc.5,bisoc.6,
          bisoc.8,
          bisoc.9,bisoc.10,
             bisoc.11,bisoc.12,
             bisoc.13),
        custom.coef.names = coef.names.multi,
        naive = TRUE,
        inline.css = TRUE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        include.pvalues=TRUE,
        caption="Bivariate social blame", caption.above=TRUE)

@@

library(texreg)
htmlreg(list(biind.1,biind.2,
          biind.3,biind.4,
          biind.5,biind.6,
          biind.8,
          biind.9,biind.10,
          biind.11,biind.12,
             biind.13),
        custom.coef.names = coef.names.multi,
        naive = TRUE,
        inline.css = TRUE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        use.packages=FALSE,
        include.pvalues=TRUE,
        caption="Bivariate individual blame", 
        caption.above=TRUE)

@@

htmlreg(list(soc.0,
        soc.1,
        soc.2,
        soc.3,
        soc.4),
        custom.model.names = model.names.multi,
        custom.coef.names = coef.names.multi,
        naive = TRUE,
        inline.css = TRUE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        include.pvalues=TRUE,
        caption="Logistic multilevel random intercept model for social blame type of explanation", 
        caption.above=TRUE)

@@

```{rmultilevelMultiIndOutputNOCI, results='asis'}
htmlreg(list(ind.0,
       ind.1,
       ind.2,
       ind.3,
       ind.4),
        custom.model.names = model.names.multi,
        custom.coef.names = coef.names.multi,
        naive = TRUE,
        ci.test = NULL,
        inline.css = TRUE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        include.pvalues=TRUE,
        caption="Logistic multilevel random intercept model for individual blame type of explanation", 
        caption.above=TRUE)

@@

library(texreg)
htmlreg(list(soc.4,ind.4,socVsInc),
        naive = TRUE,
        custom.model.names = model.names.multi.2,
        custom.coef.names = coef.names.multi,
        inline.css = TRUE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        include.pvalues=TRUE,
        caption="Logistic multilevel random intercept model for social and individual blame type of explanation", 
        caption.above=TRUE)
```
